Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-06-29 manuscript/main.tex
before gym

%	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$. Let 
	\begin{proposition} \label{Proposition: generalized rayleigh quotient}
		  For any unit-length direction in $\mathcal{H}$
		  whose functional parts lie in $\operatorname{span}(\Phi^{(1)}), \ldots, \operatorname{span}(\Phi^{(K)})$,
		let us define
		the empirical and basis-approximated sample covariance between the resulting component and response as
\begin{equation*}
	\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )
	:=
	\frac{1}{n} 
	\mathbf{y}^\top 
 \langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_\mathcal{H},
\end{equation*}
where right-hand side notation comes from Definition \ref{def:n_one_inner_product}.
Then the PLS direction 
$	\hat{\boldsymbol{\xi}}$ 
 computed in \eqref{def:computed_PLS_direction} maximizes $\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )$.
	\end{proposition}

>>>>

%	consider the basis function expansions of the functional predictors $X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)$, $i=1, \ldots, n$, and those of the functional parts of the PLS component $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k)$, $k=1, \ldots, K$. Let 
	\begin{proposition} \label{Proposition: generalized rayleigh quotient}
		  For any unit-length direction in $\mathcal{H}$
		  whose functional parts lie in $\operatorname{span}(\Phi^{(1)})$, $\ldots,$ $\operatorname{span}(\Phi^{(K)})$,
		let us define
		the empirical and basis-approximated sample covariance between the resulting component and response as
\begin{equation*}
	\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )
	:=
	\frac{1}{n} 
	\mathbf{y}^\top 
 \langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_\mathcal{H},
\end{equation*}
where right-hand side notation comes from Definition \ref{def:n_one_inner_product}.
Then the PLS direction 
$	\hat{\boldsymbol{\xi}}$ 
 computed in \eqref{def:computed_PLS_direction} maximizes $\widehat{\textnormal{Cov}} (\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}, Y )$.
	\end{proposition}
